---
title: "Untitled"
author: "Vinoth Aryan Nagabosshanam"
date: "May 20, 2017"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---
# step to create a list 
```{r}
list1<-list(1,2,3,4,5,6,6,6,7)

print(typeof(list1))
```

# to create a martic 
```{r}
a<-c(1,2,3,4,5)
b<-c(6,7,8,9,10)

m<-matrix(c(a,b),nrow=2,byrow=T)
print(m)
```

# create a data frame
```{r}
a<-c(1,2,3,4,5)
b<-c('a','b','c','d','e')
c<-c('vino','in','gggg','jjj','hhh')

df<-data.frame(a,b,c)
print(typeof(df))

df
```

#sequence  its give the print space sequence 
```{r}
v<-seq(1,10,1)
v
v1<-seq(1,20, 2)
v1

v2<-seq(1,10,3)
v2
```

# square
```{r}
a1<-c(10,11,12)
sqrt(a1)
```

# defeine a function
```{r}
cube<-function(x){x*x*x}
cube(3)

```
# step import the csv

```{r}
mba<-read.csv("B:\\data science course of udemy\\Datasets_BA 2\\mba.csv")
# to get name of colunms in list
ls(mba)

fraudata<-read.csv("B:\\data science course of udemy\\Datasets_BA 2\\fraudData.csv")
# to get the first 10 lines of data
head(fraudata)
#to list names
ls(fraudata)
#summary of data set

summary(fraudata)
# to get the type of colunms in data set
str(fraudata)
```

# basic function can done in the data set 

```{r}


or<-order(fraudata$creditLine)

# to arrange the creditline in order maner we use this command
fraudata[or,]


#to arrange int descending order
fraudata[rev(order(fraudata$creditLine)),]

```

# combine the different data set
```{r}
plasma<-read.csv("B:\\data science course of udemy\\Datasets_BA 2\\Plasma.csv")
diec<-read.csv("B:\\data science course of udemy\\Datasets_BA 2\\Diabetes.csv")
pd<-cbind(plasma,diec)
```

# if its un equal
```{r}
tran_h<-read.csv("B:\\data science course of udemy\\Datasets_BA 2\\hour_transaction.csv")
tran_d<-read.csv("B:\\data science course of udemy\\Datasets_BA 2\\transaction_data.csv")
tt<-rbind(tran_h,tran_d)

```

# if both unequal we use merge function
```{r}
all_tran<-read.csv("B:\\data science course of udemy\\Datasets_BA 2\\all_transactions.csv")
cre<-read.csv("B:\\data science course of udemy\\Datasets_BA 2\\creditdata.csv")

slc<-merge(all_tran,cre)
```

# to read text file by using following command
```{r}
vitcims<-readLines("B:\\data science course of udemy\\Datasets_BA 2\\victims.txt")
vitcims

dfv<-data.frame(vitcims)
dfv

# grepl which used to find extact sentence 
com<-grepl("^%", vitcims)
com

# we are viewing without those element
text<-vitcims[!com]
text
# code used to split lines in colunms
out <- strsplit(text,',')

# step convert in data fram
nl<-matrix(unlist(out),nrow=length(out),byrow = T)
# assign col names
colnames(nl)<-c("name","birthyear","deathyear")
ti_victims<-as.data.frame(nl)
summary(nl)

# to conver year into numer
ti_victims$birthyear <-as.numeric(ti_victims$birthyear)
ti_victims$deathyear<-as.numeric(ti_victims$deathyear)
summary(ti_victims)
str(ti_victims)

```

```{r}
telecalls<-read.csv("B:\\data science course of udemy\\Datasets_BA 2\\telecomCalls.csv")
```

# replace negative values in colums with na values
```{r}
upd_tel<-apply(telecalls,MARGIN = 2,
               function(a)
                 {ifelse (a==99|a==-99, NA,a)})
upd_tel
```


# now clear the NA with mean valur
```{r}
apply(upd_tel,MARGIN = 2,function(a){mean(a,na.rm = T)})

library(zoo)
na.aggregate(upd_tel)
```

# install lattice package
```{r}
library("lattice")
data(barley)
tapply(barley$yield,barley$site, mean)
```

#  how to pload othe rthe stastical package
```{r}
library("foreign")

can<-read.spss("B:\\data science course of udemy\\Datasets_BA 2\\cancer.sav")

cans<-as.data.frame(can)
str(cans)
summary(cans)
# step to fill the na value with median
cans$TOTALCW6[is.na(cans$TOTALCW6)]<-median(cans$TOTALCW6,na.rm=TRUE)
summary(cans)

cor(cans)
```

#to check the correlation and covariance between the dataset by using corrgram
```{r}
#install.packages("corrgram")
library(corrgram)
corrgram(cans)
# red color incidates the negative correlation 
# blue color incidates the postive correlation
```

